\documentclass[11pt, a4paper]{article}

% ── Encoding & fonts ────────────────────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ── Layout ──────────────────────────────────────────────────────────────
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\onehalfspacing

% ── Tables ──────────────────────────────────────────────────────────────
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{graphicx}          % \resizebox
\usepackage{makecell}

% ── Math ────────────────────────────────────────────────────────────────
\usepackage{amsmath, amssymb}

% ── Check/cross marks ──────────────────────────────────────────────────
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

% ── Hyperlinks ──────────────────────────────────────────────────────────
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}

% ── Headers ─────────────────────────────────────────────────────────────
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small Multi-Agent LLM Pipeline Ablation Study}
\fancyhead[R]{\small \today}
\fancyfoot[C]{\thepage}

% ── Title ───────────────────────────────────────────────────────────────
\title{%
  Multi-Agent LLM Pipeline Ablation Study:\\
  Cost--Accuracy Trade-offs in Automated Journal Entry Generation%
}
\author{Autobook --- CSC490}
\date{\today}

\begin{document}

\maketitle

% ── Abstract ────────────────────────────────────────────────────────────
\begin{abstract}
This report presents an ablation study of a multi-agent LLM pipeline for
automated double-entry journal entry generation. We evaluate six pipeline
variants---from a single-agent baseline to a full eight-agent pipeline with
disambiguation, classification, correction, and evaluation---across basic,
intermediate, and hard accounting test cases. We measure exact-match accuracy,
slot-level accuracy, decision correctness, cost efficiency (cost-of-pass),
token consumption, cache utilization, latency distribution, and multi-run
consistency. Marginal component analysis quantifies the accuracy--cost
trade-off of each pipeline stage.
\end{abstract}

\tableofcontents
\newpage

% ── 1. Introduction ────────────────────────────────────────────────────
\section{Introduction}

The Autobook system converts natural-language transaction descriptions into
IFRS-compliant double-entry journal entries using a configurable multi-agent
LLM pipeline. The pipeline decomposes the task into disambiguation,
classification (debit/credit 6-tuples), cross-validation, entry construction,
approval, and diagnostic repair.

Three ablation flags control which agents are active:
\texttt{disambiguator\_active}, \texttt{correction\_active}, and
\texttt{evaluation\_active}. This yields eight possible pipeline variants,
of which six are evaluated in this study (five multi-agent variants plus a
single-agent baseline).

% ── 2. Methodology ─────────────────────────────────────────────────────
\section{Methodology}

\subsection{Variants}
\begin{itemize}
  \item \textbf{single\_agent}: One LLM call classifies and builds the entry.
  \item \textbf{baseline} (D=off, C=off, E=off): Classifiers + entry builder only.
  \item \textbf{with\_correction} (D=off, C=on, E=off): Adds cross-validation correctors.
  \item \textbf{with\_evaluation} (D=off, C=off, E=on): Adds approver + diagnostician + fix loop.
  \item \textbf{with\_disambiguation} (D=on, C=off, E=off): Adds disambiguator.
  \item \textbf{full\_pipeline} (D=on, C=on, E=on): All agents active.
\end{itemize}

\subsection{Test Cases}
Test cases span three difficulty tiers:
\begin{itemize}
  \item \textbf{Basic} (15 cases): Unambiguous single- and multi-line entries.
  \item \textbf{Intermediate} (27 cases): Complex capitalization, tax handling,
        present value, compound entries.
  \item \textbf{Hard} (5 cases): Genuinely ambiguous transactions requiring
        clarification (multiple valid interpretations).
\end{itemize}

\subsection{Metrics}
Following recent multi-agent evaluation methodology
\cite{multiagentbench2025, efficient-agents2025, financial-benchmark2026},
we measure:
\begin{enumerate}
  \item \textbf{Exact match rate}: Both debit and credit tuples match expected.
  \item \textbf{Slot accuracy}: Per-slot correctness averaged across tuples.
  \item \textbf{Decision accuracy}: Pipeline decision (Approved/Incomplete/Stuck) matches expected.
  \item \textbf{Entry validity}: Debits equal credits, valid account types.
  \item \textbf{Cost-of-pass}: Cost per correctly classified transaction.
  \item \textbf{Token efficiency}: Output tokens / total tokens consumed.
  \item \textbf{Cache hit rate}: Cache-read tokens / total input tokens.
  \item \textbf{Latency}: p50 and p95 end-to-end latency.
  \item \textbf{Marginal value}: Per-component accuracy $\Delta$ vs cost $\Delta$.
  \item \textbf{Multi-run consistency}: $\mu \pm \sigma$ across repeated runs.
\end{enumerate}

% ── 3. Results ──────────────────────────────────────────────────────────
\section{Results}

\subsection{Variant Comparison}
\input{component/variant_comparison}

\subsection{Accuracy by Difficulty Tier}
\input{component/tier_breakdown}

\subsection{Marginal Component Value}
\input{component/marginal_deltas}

\subsection{Per-Test-Case Breakdown}
\input{component/per_test_case}

\subsection{Per-Agent Resource Consumption}
\input{component/agent_breakdown}

\subsection{Multi-Run Consistency}
\input{component/consistency}

% ── 4. Discussion ──────────────────────────────────────────────────────
\section{Discussion}

% Analysis of results goes here.
% Key questions to address:
% - Which component contributes the most accuracy per dollar?
% - Is the correction pass worth its cost?
% - Does the fix loop recover meaningful errors?
% - How does disambiguation affect hard-case handling?
% - Is the pipeline more cost-effective than the single-agent baseline?

% ── 5. Conclusion ──────────────────────────────────────────────────────
\section{Conclusion}

% Summary of findings and recommended production configuration.

% ── References ──────────────────────────────────────────────────────────
\begin{thebibliography}{9}

\bibitem{multiagentbench2025}
  MultiAgentBench: Evaluating the Collaboration and Competition of LLM Agents.
  \textit{arXiv:2503.01935}, March 2025.

\bibitem{efficient-agents2025}
  Efficient Agents: Building Effective Agents While Reducing Cost.
  \textit{arXiv:2508.02694}, 2025.

\bibitem{financial-benchmark2026}
  Benchmarking Multi-Agent LLM Architectures for Financial Document Processing.
  \textit{arXiv:2603.22651}, March 2026.

\bibitem{kdd-survey2025}
  Evaluation and Benchmarking of LLM Agents: A Survey.
  \textit{KDD 2025}.

\end{thebibliography}

\end{document}
